---
title: "SvX data and stats"
author: "Pablo Maldonado"
date: "9/28/2023"
output:
  html_document: default
  word_document: default
  pdf_document: default
editor_options:
  chunk_output_type: inline
---

```{r global options}
knitr::opts_chunk$set(echo = TRUE, error = FALSE, message = FALSE, warning = FALSE)

```

## Loading packages

```{r message=FALSE, warning=FALSE, include=FALSE}
library(jtools)
library(readxl)
library(ggplot2)
library(RColorBrewer)
library(dplyr)
library(tidyverse)
library(scales)
library(stringr)
library(tidyr)
library(knitr)
library(forcats)
library(broom)
library(ggfortify)
library(stats)
library(ggpubr)
library(grDevices)
library(rstatix)
library(writexl)
library(purrr)
library(kableExtra)
library(ggbeeswarm)
library(multcomp)
library(DescTools)
library(car)
library(exactRankTests)
library(readr)
library(ggeffects)
library(GGally)
library(gridExtra)
library(emmeans)
#mm7qNhXs8FN4CFS
```

MULTI CSV SHEETS MALE FEMALE
```{r echo=TRUE, message=FALSE, warning=FALSE}
# Read in all CSV files
files <- list.files(path = "/Volumes/cvmbs/RSTOR-HenaO_lab/SolaVAX-TB/SvX_R_analysis/BAL", pattern = "*.csv", full.names = TRUE)

dfs <- lapply(files, function(file) {
  # Read the CSV file and clean up column names
  df <- read_csv(file)
    df <- df %>%
    rename("Sample" = colnames(.)[1]) %>%
    dplyr::select(Sample, contains("Count")) %>%
    rename_all(funs(str_replace(., "\\|.+", ""))) %>%
    rename_all(~ str_remove(., "Leukocytes/Single Cells/")) %>%
    rename_all(~ str_remove(., "Leukocytes/")) %>%
    rename_all(~ str_remove(., "LIVE/")) %>%
    # mutate(Sample = str_replace_all(Sample, "\\b[A-Za-z][0-9]+\\b", "")) %>%
    rename_all(funs(str_replace_all(., ",", ""))) %>%
    rename_all(funs(str_replace_all(., "/", " "))) %>%
    rename_all(funs(str_replace_all(., "\\\\", " ")))  %>%
    rename_all(~ stringr::str_replace_all(., "Q\\d+\\:", "")) %>%
    rename("cells in sample" := matches("Count")) %>%
    rename("leukocytes" := matches("Leukocytes")) %>%
    rename("live leukocytes" := matches("LIVE")) %>%
    rename("single cells" := matches("Single Cells")) %>%
  # Removing logical vectors, not sure why its adding these
  dplyr::select(where(~ !any(is.logical(.)) | is.numeric(.))) %>%
  # Remove last two rows of SD and Mean
  slice(1:(n() - 2))
  # Extract the sex from the file name
  sex <- ifelse(grepl("female", file), "female", "male")
  df <- df %>% mutate(sex = sex)
  # Move the sex column to the second position
  df <- df %>% relocate(sex, .after = 1)
  # Extract the day from the file name
  day <- str_extract(file, "(?<=Day\\s)\\d+")
  df <- df %>% mutate(day = as.character(day))
  # Move the day column to the third position
  df <- df %>% relocate(day, .after = 2)
  
  return(df)
})

# Combine all data frames into one dataframe
Df1 <- bind_rows(dfs)
Df1

#str(dfs)
#tail(Df1)

# Check for NA values in Df1
#na_counts <- colSums(is.na(Df1))

# Print the column names with NA counts
#print(na_counts)
Df1
```

## MAKING DATA TIDY
```{r echo=TRUE, message=FALSE, warning=FALSE}
tidy_Df1 <- pivot_longer(data = Df1, cols =  starts_with(" CD11"), names_to = "cell_types", values_to = "cell type count")

# Fix Sample Column
tidy_Df1 <- tidy_Df1 %>%
  mutate(Sample = gsub("^[A-Za-z]\\d{1,2}\\s", "", Sample))



tidy_Df1 <- tidy_Df1 %>%
  separate(col = "Sample", into = c("group", "mouse_ID"), sep = " ") %>%
  mutate(mouse_ID = str_replace(mouse_ID, ".fcs", ""))

tidy_Df1$group <- str_replace_all(tidy_Df1$group, "-", " ")

# Trim extra spaces
tidy_Df1$cell_types <- str_replace_all(tidy_Df1$cell_types, "\\s+", " ")
tidy_Df1$cell_types <- str_trim(tidy_Df1$cell_types)
tidy_Df1$group <- trimws(tidy_Df1$group)


tidy_Df1 



# Change Names 
tidy_Df1 <- tidy_Df1 %>%
  mutate(group = case_when(
    group == "IN+INULIN" ~ "SvX IN + Inulin",
    group == "IN+Inulin" ~ "SvX IN + Inulin",
    group == "IM+CPG" ~ "SvX IM + CpG",
    TRUE ~ group  # Keep other values as they are
  ))

# call all group names
tidy_Df1 %>%
  dplyr::select(group) %>%
  distinct()

tidy_Df1
```

## Insert trials and successes (cell counts and parent populations)
```{r echo=TRUE, message=FALSE, warning=FALSE}
# Filter CD19- B220- CD3+ CD8- CD4+, CD19- B220- CD3+ CD8- CD4+ CD44+ CD62L- to find trials and successes
tidy_Df1$cell_types [3]
t_cell_activation <- tidy_Df1 %>%
  dplyr::filter(cell_types == "CD11C+ CD45+" | cell_types == "CD11C+ CD45+ CD44+ MHCII+") 

t_cell_activation <- t_cell_activation %>%
  pivot_wider(names_from = cell_types, values_from = `cell type count`) %>%
  rename(trials = "CD11C+ CD45+", successes = "CD11C+ CD45+ CD44+ MHCII+") %>%
  mutate(failures = trials - successes) %>%
  dplyr::select(-`cells in sample`, -leukocytes, -`single cells`)

#t_cell_activation <- t_cell_activation %>%
 #   filter(!(group == "Saline" & mouse_ID == 2 & day == "30"))
t_cell_activation

t_cell_activationPLOT <- t_cell_activation
t_cell_activationPLOT <- t_cell_activationPLOT %>%
  mutate(proportion_of_activated_tcells = (successes/trials*100)) 


# Assuming 't_cell_activation' is your data frame
t_cell_activation$log_trials <- log(as.numeric(t_cell_activation$trials))
t_cell_activation$successes  <- log(as.numeric(t_cell_activation$successes ))
t_cell_activation$failures <- log(as.numeric(t_cell_activation$failures))

```
#Better than BCG?
#does sex matter?
#key immune populations?

# Set reference group
```{r echo=TRUE, message=FALSE, warning=FALSE}
# Convert 'result' into a factor data type.
t_cell_activation$successes <- as.factor(t_cell_activation$successes)
# Convert 'group' into a factor data type.
t_cell_activation$group <- factor(t_cell_activation$group)
# Convert 'day' into a factor data type.
t_cell_activation$day <- as.factor(t_cell_activation$day)
t_cell_activation$failures <- as.factor(t_cell_activation$failures)
t_cell_activation$sex <- as.factor(t_cell_activation$sex)

# Reorder groups for visuals
t_cell_activation <- t_cell_activation %>%
  mutate(group = fct_relevel(group, "Saline", "BCG", "BCG BCG", "SvX IN + Inulin", "SvX IM + CpG"))
t_cell_activation$group <- relevel(t_cell_activation$group, ref = "Saline")

```


## Detecting outliers based on group and sex
```{r eval=FALSE, include=FALSE}
# # Create a sample data frame
# 
# outliersubset_data <- t_cell_activationPLOT
# 
# 
# detect_outliers_within_group_sex <- function(dataframe, column, group_column, sex_column) {
#   
#     if (!(column %in% colnames(dataframe))) {
#     stop("Column not found in the dataframe")
#   }
#   
#   if (!(group_column %in% colnames(dataframe))) {
#     stop("Grouping column not found in the dataframe")
#   }
#   
#   if (!is.numeric(dataframe[[column]])) {
#     stop("Column must contain numeric data")
#   }
#   
# # Group by the "group" and "sex" columns
#   grouped_data <- dataframe %>%
#     group_by(!!sym(group_column), !!sym(sex_column)) %>%
#     summarise(
#       Quantile1 = quantile(!!sym(column), probs = 0.25),
#       Quantile3 = quantile(!!sym(column), probs = 0.75),
#       IQR = Quantile3 - Quantile1,
#       .groups = "drop"
#     )
#   
#   # Left join the grouped data with the original dataframe
#   sample_dataIQR <- dataframe %>%
#     left_join(grouped_data, by = c(group_column, sex_column))
#   
#   # Filter for outliers
#   outliers <- sample_dataIQR %>%
#     group_by(!!sym(group_column), !!sym(sex_column)) %>%
#     filter(!!sym(column) > (Quantile3 + IQR * 1.5) | !!sym(column) < (Quantile1 - IQR * 1.5))
#   
#   if (nrow(outliers) > 0) {
#     # Return the rows containing outliers in the specified column
#     return(outliers)
#   } else {
#     message("No outliers found in the specified column.")
#     return(NULL)
#   }
# }
# 
# 
# # Usage
# detect_outliers_within_group_sex(outliersubset_data, "proportion_of_activated_tcells", "group", "sex")
```


## Detecting outliers based on group ONLY
```{r eval=FALSE, include=FALSE}
# 
# detect_outliers_within_group <- function(dataframe, column, group_column) {
#   
#     if (!(column %in% colnames(dataframe))) {
#     stop("Column not found in the dataframe")
#   }
#   
#   if (!(group_column %in% colnames(dataframe))) {
#     stop("Grouping column not found in the dataframe")
#   }
#   
#   if (!is.numeric(dataframe[[column]])) {
#     stop("Column must contain numeric data")
#   }
#   
# # Group by the "group" and "sex" columns
#   grouped_data <- dataframe %>%
#     group_by(!!sym(group_column)) %>%
#     summarise(
#       Quantile1 = quantile(!!sym(column), probs = 0.25),
#       Quantile3 = quantile(!!sym(column), probs = 0.75),
#       IQR = Quantile3 - Quantile1)
#   
#   # Left join the grouped data with the original dataframe
#   sample_dataIQR <- dataframe %>%
#     left_join(grouped_data, by = group_column)
#   
#   # Filter for outliers
#   outliers <- sample_dataIQR %>%
#     group_by(!!sym(group_column)) %>%
#     filter(!!sym(column) > (Quantile3 + IQR * 1.5) | !!sym(column) < (Quantile1 - IQR * 1.5))
#   
#   if (nrow(outliers) > 0) {
#     # Return the rows containing outliers in the specified column
#     return(outliers)
#   } else {
#     message("No outliers found in the specified column.")
#     return(NULL)
#   }
# }
# 
# detect_outliers_within_group(outliersubset_data, "proportion_of_activated_tcells", "group")



# Revome outliers OPTIONAL
# 
# t_cell_activation_outliers <- outliersubset_data %>%
#   filter(!(group == "Saline" & mouse_ID == "2" & sex == "female" & day == "14") &
#          !(group == "BCG" & mouse_ID == "1" & sex == "female" & day == "14"))
```

## GLM modeling for: group * day + sex | group * day * sex | group * day
```{r echo=TRUE}
#log(p / (1 - p)) = β₀ + β₁*Saline + β₂*ID93 + β₃*BCG+ID93 + β₄*day56 + β₅*sexmale + β₆*(Saline * day56) + β₇*(ID93 * day56) + β₈*(BCG+ID93 * day56) + β₉*(Saline * sexmale) + β₁₀*(ID93 * sexmale) + β₁₁*(BCG+ID93 * sexmale)
l_mod1 <- glm(cbind(successes, failures) ~ group * day, 
              family = quasibinomial(link = "logit"), data = t_cell_activation)
summary(l_mod1)



# # log(p / (1 - p)) = β₀ + β₁*Saline + β₂*ID93 + β₃*BCG93 + β₄*Male + β₅*Day56 + β₆*(Saline * Male) + β₇*(ID93 * Male) + β₈*(BCG93 * Male) + β₉*(Saline * Day56) + β₁₀*(ID93 * Day56) + β₁₁*(BCG93 * Day56) + β₁₂*(Saline * Male * Day56) + β₁₃*(ID93 * Male * Day56) + β₁₄*(BCG93 * Male * Day56)
l_mod2 <- glm(cbind(successes, failures) ~ group + day,
              family = quasibinomial(link = "logit"), data = t_cell_activation)
summary(l_mod2)

```


## Drop-in-deviance test to compare models

# CAN WE LEAVE OUT SEX BASED ON SIGNIFICANCE?
```{r echo=TRUE}
drop_in_dev1 <- anova(l_mod1, l_mod2, test = "Chisq")



drop_in_dev1 

# choose lmod_2, changing to lmod_1 for ease of code

l_mod1 <- glm(cbind(successes, failures) ~ group * day, 
              family = quasibinomial(link = "logit"), data = t_cell_activation)


```


## Cook's D (Cook's distance) is a statistical measure used in regression analysis to quantify the influence of individual data points (observations) on the model's parameter estimates. It helps identify observations that, if removed from the dataset, would lead to significant changes in the estimated coefficients or model predictions. In essence, Cook's D indicates how much a specific data point affects the overall regression model.
```{r echo=TRUE}
# # Calculate Cook's distance
# cooksd <- cooks.distance(l_mod1)
# 
# # Define a threshold for influential points (e.g., 4/n)
# threshold <- 4 / length(cooksd)
# 
# # Identify influential observations (those with Cook's distance above the threshold)
# influential <- cooksd > threshold
# 
# # Create a scatterplot to visualize outliers and influential points
# plot(cooksd, pch = 19, cex = 1, main = "Cook's Distance Plot")
# abline(h = threshold, col = "red") # Add a horizontal line at the threshold
# 
# # Color the points to differentiate between outliers and influential points
# points(which(influential), cooksd[influential], col = "red", pch = 19)
# points(which(!influential), cooksd[!influential], col = "blue", pch = 19)
# 
# # Add legend
# legend("topright", legend = c("Influential", "Not Influential"),
#        col = c("red", "blue"), pch = 19)
# 
# # Identify the indices of influential points
# influential_indices <- which(cooksd > threshold)
# 
# t_cell_activation_CD1 <- t_cell_activation[-influential_indices, ]
# t_cell_activationPLOT <- t_cell_activationPLOT[-influential_indices, ]
# 
# l_mod1 <- glm(cbind(successes, failures) ~ group * day,
#               family = quasibinomial(link = "logit"), data = t_cell_activation_CD1)
# 
# summary(l_mod1)
# 
# 
# t_cell_activation[influential_indices, ]
```


```{r eval=FALSE, include=FALSE}
# # Specify the number of folds (e.g., 10-fold cross-validation)
# num_folds <- 10
# 
# # Perform k-fold cross-validation
# cv_results <- train(
#   x = t_cell_activation[, c("group", "day", "sex")],  # Predictors
#   y = t_cell_activation[, c("successes", "failures")],  # Response
#   method = "glm",  # Specify the modeling method
#   trControl = trainControl(
#     method = "cv",  # Cross-validation method
#     number = num_folds  # Number of folds
#   ),
#   glmFamily = quasibinomial(link = "logit")  # Family argument for GLM
# )
# 
# # Access cross-validation results
# summary(cv_results)
```

## Model diagnostics 
## Plots involving the residuals are used for assessing the validity of the model assumptions for GLMs.
```{r echo=TRUE}
# Create a residual vs fitted plot
residuals <- residuals(l_mod1)
fitted_values <- fitted(l_mod1)
group <- t_cell_activation$group
# Create the residuals vs. fitted plot
plot(fitted_values, residuals, main = "Residuals vs. Fitted", 
     xlab = "Fitted Values", ylab = "Residuals")
text(fitted_values, residuals, labels=group, pos=3)

# Add a horizontal reference line at y = 0 (optional)
abline(h = 0, col = "red", lty = 2)

# Create a QQ plot of deviance residuals
qqnorm(residuals)
qqline(residuals)


# Check for overdispersion
ratio_deviance_df <- residuals(l_mod1, type = "deviance")^2 / df.residual(l_mod1)
sum(ratio_deviance_df) / df.residual(l_mod1)





```

## GLM modeling and plotting expected outcomes of group * day + sex
```{r echo=TRUE}
#Plot and interpret effects
plotGroup <- effect_plot(l_mod1, pred = group, interval = TRUE, y.label = "Probability of Activated T-cells")
plotDay <- effect_plot(l_mod1, pred = day, interval = TRUE, y.label = "Probability of Activated T-cells")

grid.arrange(plotGroup, plotDay, ncol = 3)

# Calculate the probabilities for all combinations using testMod
combinations <- expand.grid(day = levels(t_cell_activation$day),
                            group = levels(t_cell_activation$group))

results <- combinations %>%
  rowwise() %>%
  mutate(probability = predict(l_mod1, newdata = data.frame(day, group), type = "response"))

# Create a heatmap

ggplot(results, aes(x = day, y = group)) +
  geom_tile(aes(fill = probability)) +
  #facet_grid(. ~ sex, scales = "free_y") +
  scale_fill_gradient(low = "lightblue", high = "darkblue") +
  labs(x = "Day", y = "Group", fill = "Probability of Activated T-cells") +
  theme_minimal()

#plot coefficients
coefficients <- summary(l_mod1)$coefficients[, c("Estimate", "Std. Error")]

# Create a data frame
coefficients_df <- data.frame(
  Variable = rownames(coefficients),
  Estimate = coefficients[, "Estimate"],
  SE = coefficients[, "Std. Error"]
)

# plot it
ggplot(coefficients_df, aes(x = reorder(Variable, Estimate), y = Estimate, ymin = Estimate - 1.96 * SE, ymax = Estimate + 1.96 * SE)) +
  geom_pointrange() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
  coord_flip() +
  labs(title = "Coefficients and Confidence Intervals",
       x = "Variable",
       y = "Estimated Coefficient") +
  theme_minimal()

# Create predicted probabilities for all variables
predictor_terms <- c("day", "group")
predictions <- ggpredict(l_mod1, terms = predictor_terms)
plot(predictions)
```


# Calculate the odds ratios and plot 
```{r echo=TRUE}

# l_mod1 <- glm(cbind(successes, failures) ~ group * day, 
#               family = quasibinomial(link = "logit"), data = t_cell_activation)

CI <- exp(confint(l_mod1))
# Extract coefficients
coefficients <- summary(l_mod1)$coef

# Define a significance threshold (e.g., 0.05)
significance_threshold <- 0.05


# Subset coefficients based on significance threshold
significant_coefficients <- coefficients[coefficients[, 4] < significance_threshold, , drop = FALSE]

# Extract row names
significant_row_names <- rownames(coefficients)[coefficients[, 4] < significance_threshold]

# Set row names for the significant coefficients
rownames(significant_coefficients) <- significant_row_names

# Filter significant coefficients
#significant_coefficients <- coefficients[coefficients[, 4] < significance_threshold, ]

# Calculate odds ratios
odds_ratios <- exp(significant_coefficients[, 1])

odds_ratios <- data.frame(Odds_Ratio = odds_ratios)
rownames(odds_ratios) <- significant_row_names



odds_ratios <- as.data.frame(odds_ratios) %>% 
    rownames_to_column('Variable')
CI_df <- as.data.frame(CI) %>%
    rownames_to_column('Variable')


odds_ratios <- inner_join(odds_ratios, CI_df, by = "Variable")
odds_ratios$Variable <- gsub("^group", "", odds_ratios$Variable)
odds_ratios <- odds_ratios %>%
  filter(Variable != "(Intercept)")

odds_ratios
```

```{r echo=TRUE}

# Extract the CI values
variables <- odds_ratios[, 1] 
odds_ratio <- odds_ratios[, 2]
lower_ci <- odds_ratios[, 3] 
upper_ci <- odds_ratios[, 4]


odds_data <- data.frame(
  variables = variables,
  odds_ratio = odds_ratio,
  lower_ci = lower_ci,
  upper_ci = upper_ci)

# Reorder the order of "odds_ratios"
odds_data$variables <- factor(odds_data$variables, levels = odds_data$variables[order(odds_data$odds_ratio)])

# Create a plot

ggplot(odds_data, aes(x = odds_ratio, y = variables)) +
  geom_point() +
  geom_errorbarh(aes(xmin = lower_ci, xmax = upper_ci), height = 0) +
  labs(title = "Odds Ratios with 95% Confidence Intervals",
       x = "Odds Ratio",
       y = "Variable") +
    scale_x_continuous(breaks = c(0, 1, 2, 5)) +
   geom_text(aes(label = round(odds_ratio, 2)), vjust = -0.5)
```


# Plot actual CD4+ CD44+ populations for comparison to predicited outcomes
```{r echo=FALSE}
# Plot: Group Comparison of Activated T-cells (Combined Days)
t_cell_activationPLOT %>%
  mutate(group = fct_relevel(group, "Saline", "BCG", "BCG BCG", "SvX IN + Inulin", "SvX IM + CpG")) %>%
  ggplot(aes(x = group, y = proportion_of_activated_tcells, fill = group, color = group)) +
  geom_boxplot(width = 0.5, alpha = 0.5, position = position_dodge(width = 0.75)) +
  geom_point(size = 3, shape = 21, alpha = 0.8, na.rm = TRUE, color = "black",
             position = position_dodge(width = 0.75)) +
    labs(title = "CD4+ CD44+ Tcells", x = "Group", y = "% activated T-cells (normalized to CD4+)", color = "Vaccine") +
  guides(fill = "none", shape = guide_legend(title = "Vaccine")) +
  theme_bw() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 

# # Plot: Group Comparison of Activated T-cells (Facet-wrapped by Day)
# t_cell_activationPLOT  %>%
#   mutate(group = fct_relevel(group, "Saline", "BCG", "BCG BCG", "SvX IN + Inulin", "SvX IM + CpG")) %>%
#   ggplot(aes(x = group, y = proportion_of_activated_tcells, fill = group, color = group)) +
#   geom_boxplot(width = 0.5, alpha = 0.5, position = position_dodge(width = 0.75)) +
#   geom_point(size = 3, shape = 21, alpha = 0.8, na.rm = TRUE, color = "black",
#              position = position_dodge(width = 0.75)) +
#     labs(title = "CD4+ CD44+ Tcells", x = "Group", y = "% activated T-cells (normalized to CD4+)", color = "Vaccine") +
#   guides(fill = "none", shape = guide_legend(title = "Vaccine")) +
#   theme_bw() + 
#   theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
#   facet_wrap(~ day, scales = "free_y", ncol = 4, strip.position = "top")


# Plot: Activated T-cells by Sex (Group Comparison with t-tests)
t_cell_activationPLOT  %>%
  mutate(group = fct_relevel(group, "Saline", "BCG", "BCG BCG", "SvX IN + Inulin", "SvX IM + CpG")) %>%
  ggplot(aes(x = day, y = proportion_of_activated_tcells, fill = day, color = day)) +
  geom_boxplot(width = 0.5, alpha = 0.5, position = position_dodge(width = 0.75)) +
  geom_point(size = 3, shape = 21, alpha = 0.8, na.rm = TRUE, color = "black",
             position = position_dodge(width = 0.75)) +
  theme_bw() +
  labs(title = "Activated Tcells by Day", x = "Day", y = "% Activated T-cells (normalized to CD4+)") + 
  stat_compare_means(method = "t.test")

t_cell_activationPLOT  %>%
  mutate(group = fct_relevel(group, "Saline", "BCG", "BCG BCG", "SvX IN + Inulin", "SvX IM + CpG")) %>%
  ggplot(aes(x = day, y = proportion_of_activated_tcells, fill = group, color = group)) +
  geom_boxplot(width = 0.5, alpha = 0.5, position = position_dodge(width = 0.75)) +
  geom_point(size = 3, shape = 21, alpha = 0.8, na.rm = TRUE, color = "black",
             position = position_dodge(width = 0.75)) +
    labs(title = "CD44+ Dendritic Cells in BAL", x = "Group", y = "Proportion of CD44+ Dendritic Cells", color = "Vaccine") +
  guides(fill = "none", shape = guide_legend(title = "Vaccine")) +
  theme_bw() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 

```

```{r}
# em_means <- emmeans(l_mod1, specs = ~ group * day + sex)
# 
# # Perform pairwise comparisons using Tukey's method
# pairwise_comparisons <- emmeans::contrast(em_means, method = "pairwise", adjust = "tukey")
# 
# pairwise_comparisons <- as.data.frame(pairwise_comparisons)
# 
# # View the results of the pairwise comparisons
# significant_comparisons <- subset(pairwise_comparisons, p.value < 0.05)
```


EXPLORATORY ANALYSIS in progress
```{r eval=FALSE, fig.height=20, fig.width=10, include=FALSE}
# 
# # Running Stats and Selecting Significant Cell Type Differences for Gated Cells TukeyHSD
# cell_stats <- tidy_Df1 %>%
#    group_by(cell_types) %>%
#   nest() %>%
#   mutate(aov_result = map(data, ~aov(percentage_of_LIVE ~ group, data = .x)),
#          tukey_result = map(aov_result, TukeyHSD),
#          tidy_tukey = map(tukey_result, broom::tidy)) %>%
#   unnest(tidy_tukey, .drop = TRUE) %>%
#   separate(contrast, into = c("contrast1", "contrast2"), sep = "-") %>%
#   dplyr::select(-data, -aov_result, -tukey_result, -term, -null.value) %>%
#   filter(adj.p.value <= 0.05)
# 
# 
# # Join Dataframes Based on Significance and Cell Types
# common_cell_types <- intersect(tidy_Df1$cell_types, cell_stats$cell_types)
# tidy_Df1_filtered <- tidy_Df1 %>%
#   filter(cell_types %in% common_cell_types)
# 
# joined_df <- left_join(tidy_Df1_filtered, cell_stats, by = "cell_types")
# 
# unique(joined_df$group)
```


Saving plots to PDF
```{r eval=FALSE, include=FALSE}
# #save to pdf
# pdf(file = "/Volumes/cvmbs/RSTOR-HenaO_lab/Pablo/SOLOVAX TB/SolovaxTB immunogenicity day 14/Unmixed/FlowJo/CD45_Final_Lung_Plots.pdf",   # The directory you want to save the file in
#    width = 25, # The width of the plot in inches
#    height = 35) # The height of the plot in inches
# plot(CD45_Final_Lung_Plots)
# dev.off()
```